Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-09-14 draft.Rmd
Update draft.Rmd

**Purpose:** This article compares internal and external job mobility as a means of improving earnings growth in Germany and the UK.

@@

**Findings:** Internal and external mobility are distinctly different strategies for improving earnings. However, the institutional setting under which mobility takes place also shapes the rewards tied to mobility. In both countries the core workforce benefits form internal promotions. However, in Germany the rewards tied to internal promotion are far greater than they are in the UK. One of the reasons German workers are less mobile than British workers may have less to do with employment protection legislation and more to do with the high rewards tied to internal career ladders.

@@

**Originality/value:** Studies exploring the effects of job mobility tend to focus on single country cases. The lessons from such cases are then prescribed to other countries, without acknowledging institutional differences. Our paper articulates important differences in the mobility-earnings relationship between Germany and the UK.

>>>>

**Purpose:** The article compares internal and external job mobility as a means of improving earnings growth in Germany and the UK.

@@

**Findings:** Internal and external mobility are distinctly different strategies for improving earnings. However, the institutional setting under which mobility takes place also shapes the rewards tied to mobility. In both countries the core workforce benefits from internal promotions. However, in Germany the rewards tied to promotion are far greater than they are in the UK. A key reason German workers are less mobile than British workers may have less to do with employment protection legislation and more to do with the rewards tied to internal career ladders.

@@

**Originality/value:** Studies exploring the effects of job mobility tend to focus on single country cases. The lessons from such cases are then prescribed to other countries, without acknowledging that countries differ by capitalisms and institutional settings. Our paper articulates important differences in the mobility-earnings relationship between Germany and the UK, and helps to understand processes of inequality in both countries. German workers who are able to pursue internal promotion are likely different form those who are unable to pursue promotion. British workers also benefit from promotions, but must pursue several promotions before seeing a substantial difference in pay.

## Second abstract (different format)
